Controlling the dewetting morphologies of thin liquid films by switchable substrates

### 2022-10-03 Reply_RefereeB.tex

\documentclass[12pt,english]{article}

\usepackage{natbib}

\usepackage{graphics,graphicx,dcolumn,bm,fleqn,epic,eepic,float}
\usepackage{amssymb,amsmath,multirow,rotate,rotating,color}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
%\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\tikzset{fontscale/.style = {font=\relsize{#1}}}
\usetikzlibrary{calc}
\makeatother

\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\eqnref}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\ts}{\textsuperscript}

\definecolor{tuered}{RGB}{214,0,74}

\newcommand{\todo}[1]{\textbf{\textcolor{tuered}{ TODO: #1}}}

\newcommand{\vectornorm}[1]{\left|\left|#1\right|\right|}

\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\uvec}[1]{\hat{\vec{#1}}}
\newcommand{\tensor}[1]{\mathbf{#1}}

\definecolor{pyblue}{HTML}{1F77B4}
\definecolor{pyorange}{HTML}{FF7F0C}
\definecolor{pygreen}{HTML}{2CA02C}
\definecolor{pyred}{HTML}{D62728}

\newcommand{\JH}[1]{\textcolor{blue}{JH: #1}}
\begin{document}

% The referee PDF has been generated from r239 -- 'make referee' command.

\section*{Reply to Referee B}

We thank the Referee for his/her thorough reading of our manuscript and detailed report.
We are happy to read that the referee acknowledges the amount of work we did and thinks it could be fitting for PRL after revision.
In what follows we provide detailed answers to all Referee's questions and we discuss all the changes made to the manuscript
(which are typeset in red colour).

\begin{itemize}

\item[ \textbf{\underline{Comment 1.}}]
{
The model disjoining pressure, Eq. 3 with a tail decaying as the
inverse squared power seems odd. I am more familiar with the expected
van der Waals tail with a decay as the inverse cube power. Is there
any reason for this choice?

\item[ \textbf{Answer}]
{
The Referee is right in pointing out that, indeed, the $h^{-3}$ decay 
for the attractive part of the disjoining pressure is more straightforward 
to understand as it can be derived directly from an intermolecular potential of Lennard-Jones type. Nevertheless, it is also true that other forms
can be encountered in the literature, depending on the actual interactions
\cite{PhysRevE.63.011208}. Here, though, our choice of the $(3,2)$ pair of exponents is motivated more by computational reasons rather than by the will of 
simulating a specific liquid with given physical properties.
With such choice, in fact, the characteristic dewetting time 
is shorter, thus making the overall computational cost more manageable.
In fact, we have seen in previous study~\cite{PhysRevE.104.034801} that
except for this shift of the time scales, the dewetting dynamics remains 
qualitatively the same. To confirm this observation, we have run 
a new simulation (for a single pair of pattern wavelength and speed) 
with the $(9,3)$ exponents and show the results in figure \ref{fig:rivulets_9_3}.
\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{Figures/No_vel_render2.png}
    \caption{}
    \label{fig:rivulets9_3}
\end{figure}
We have also added a footnote in the paper commenting on this aspect.
%We thank the referee for pointing this out.
%It is true that there are variations concerning the power law model of %the disjoining pressure.
%A common one to which the referee refers to is $(n,m) = (9,3)$, the %choice we made for the manuscript is $(n,m) = (3,2)$.
%Both exponent pairs can be found in the literature with even more %variety~\cite{moulton_lega_2013,SCHWARTZ1998173,doi:10.1063/1.4828721,Br%asjen}.
%The pair $(9,3)$ is the one that can be motivated from functional %derivatives of a Lennard-Jones potential, understandably this could more %appealing to use.
%We have used both exponent pairs in previous works, see %e.g.~\cite{PhysRevE.104.034801}.
%In this manuscript we use $(3,2)$ to keep $t_0$ reasonably small and %thus the overall computational cost manageable.
%Using the pair $(9,3)$ does not alter the results, it effectively shifts %the value of $t_0$ by $\approx 10$.
}

\item[ \textbf{\underline{Comment 2.}}]
The second major concern refers to the choice of slip length. 
The authors study a fluid-substrate model that has a thin film equilibrium thickness of 
$0.07$ length units, but the slip length is one unit, hence about $10$ times larger than the equilibrium film thickness. 
This seems unexpected, in view of the small contact angle chosen for the system. 
Could the authors justify this choice?
}

\item[ \textbf{Answer}]
{
As the Referee correctly remarks, indeed small contact angles are typically associated to small slip lengths. From a phenomenological point of view, 
though, having $\delta \sim h_0$ is still commonly considered in the weak/intermediate slip regime, as proven, for instance, 
by the formation of satellite 
droplets following rivulet breakup~\cite{doi:10.1073/pnas.1820487116} or 
in the rim shape in dewetting by hole nucleation~\cite{fetzer2007quantifying, munch2005lubrication} (see also Fig.~\ref{fig:slip}).
\begin{figure}
    \centering
    \includegraphics [width=0.6\textwidth]{slip_measure.pdf}
    \caption{Dewetting rim profiles for various slip parameters $\delta$; notice the presence of a dimple behind the front, typical of 
    small to vanishing slip, which is preserved for slip lengths up to 
    $\delta \sim 10 h_0$.}
    \label{fig:slip}
\end{figure}
Our choice of this slip length value was dictated essentially by the need 
to keep numerically stability even in the strongly time dependent case 
(large pattern speed), yet remaining in a small slip regime. 
Nevertheless, motivated by the Referee's concern and in order to check that 
picture remains qualitatively the same, we have run a simulation with 
a slip length five times smaller. The results from the analysis of the Minkowski metric $q_2$, for two cases with low and high pattern speed, reveal that indeed
the droplet-to-rivulet transition is confirmed, with $\Gamma$ as the 
discriminating parameter (see figure \ref{fig:q2smallslip}).
\begin{figure}
    \centering
    %\includegraphics [width=0.6\textwidth]{slip_measure.pdf}
    \caption{}
    \label{fig:q2smallslip}
\end{figure}
We have commented on this when we give the value of the slip length, just before 
equation (5) of the revised manuscript.
%We thank the referee for bringing this up.
%Slip and disjoining pressure are an essential part of our model -- as for many %other thin film solvers.
%Here, they allow us to have moving contact lines with imposed wettability %features.
%We agree that the value may seem large at first glance.
%However, as Peschka et al. have shown, the generation of satellite droplets %during rivulet breakup, similar to what we observe, is a no-slip %feature~\cite{doi:10.1073/pnas.1820487116}.
%We observe the occurrence of satellite droplets in the initial dewetting %period.
%Increasing the slip length makes those droplets disappear.
%Another point to mention here is the dependency of the dewetting rim on the %slip.
%Small to vanishing slip induces a dimple behind the front, while for large slip %lengths this dimple vanishes~\cite{fetzer2007quantifying, %munch2005lubrication}.
%We checked this behaviour in Fig.~\ref{fig:slip} and found only a small %dependency for slip lengths $\delta < 10$.
%Spots with a thickness $h \leq h_{\ast}$ are considered dry spots, therefore %the term equilibrium thickness maybe exaturated.
}

\item[ \textbf{\underline{Comment 3.}}]
{
The relevance of the manuscript relies on the significance of the substrate's switchable properties. 
Particularly, it is assumed that the wetting properties can be modulated on space but also on time. 
The authors have mentioned in the introduction that this can be potentially done. 
However, it would be desirable that the authors relate their model of switchable substrate with some specific experimental realization, where the actual length and time scales are mentioned.
}

\item[ \textbf{{Answer}}]
{
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{simple_exp.pdf}
    \caption{Schematic realization of the experiment described in the manuscript.}
    \label{fig:experiment_illustration}
\end{figure}
We thank the Referee for bringing this up.
First, we like to note that experiments are not our field of expertise and therefore our envisioned realization could be flawed.

The idea we have would be to prepare a thin film ($h_0 \approx 4nm$ PS) on a light responsive substrate.
Dimensions of the substrate should at least be $2$ microns in $x$ and $y$, but larger is fine.
Arrange several light sources (diodes) in a lattice with a distance of $\lambda \approx 1\mu m$ between them, as displayed in Fig.~\ref{fig:experiment_illustration}.
It would be perfect if the structure on which the light sources are mounted can be moved in a periodic manner, e.g. wrapped around rolls.
On the other hand if the array of diodes is large enough, say $100\lambda$ it should be sufficient to move them continuously in one direction. 
\JH{Could one do this with a DMD as here https://doi.org/10.1021/jp301092y ? Then, one could use a transparent substrate and just do it from the bottom. I think a DMD + light responsive substrate could be a straightforward implementation of a time dependent wettability pattern.}

In Eq.~(5) we introduce two scales, $t_0$ and $v_0$.
From experiments of dewetting thin films we know that $t_0$ correlates with the rupture time~\cite{becker2003complex, PhysRevLett.99.114503}.
Considering the same experimental parameters as above, 
\begin{align*}
    t_0 &\approx 1800s,\qquad~~~\qquad \frac{2\pi}{q_0}\approx 400nm, \\
    \quad v_0 &= \frac{\lambda}{t_0} \approx \frac{1}{900}\frac{\mu m}{s},\quad \quad v_0^{\ast} = \frac{2\pi}{q_0 t_0} \approx \frac{4}{9}\frac{nm}{s},
\end{align*}
where we take into account that the rupture time is overestimated by about a factor of two.
The experiment therefore reduces to the movement of the diodes with a velocity between $[10^{-7}/900, 10^{-5}/900] m/s$. 
\JH{We need to comment on the experimental realization in the paper. Can we summarize this idea to 1-2 sentences?}
}

\item[ \textbf{\underline{Comment 4.}}]
{
An important parameter in the problem is the wave-vector $q_0$, which sets the correlation length in the problem. 
The authors should state what the actual value is relative to either the average film height, or the wave-length of modulations. 
Is there any reason to give the wave-length of modulations in units of the system size, i.e., are the results subject to finite size effects? Otherwise it appears more meaningful to describe the modulations in units of $q_0$ or the equilibrium film thickness.
}

\item[ \textbf{{Answer}}]
{
We thank the referee for this comment.
It is true that we use $q_0$ but never display its actual value.
Inserting numbers, we have 
\begin{equation*}
    q_0 \approx 0.13, \quad \lambda_0 = \frac{2\pi}{q_0} \approx 48.5 \approx \frac{L}{10},  
\end{equation*}
therefore $\lambda_0$ is usually smaller than $\lambda$.

No, these simulations do not suffer from finite size effects.
The honest reason for using multiples of the system size is the ease of the numerical realization.
Having periodic boundary conditions, a non-multiple wavelength of the system size would induce a discontinuity.
Given the complexity of the problem, we would like to have as much control of the pattern as possible.

The arbitrary choice we made had however helped us to understand where the boundary between rivulet and droplets appears.
In Eq.~(11) we use
\begin{equation*}
    \Gamma = \frac{v_{\theta}}{U_{\theta}} = \frac{\chi v_0}{U_{\theta}},
\end{equation*}
where rivulets appear for $\chi > 1$.
Substituting the wavelength dependency of $v_0$ with $q_0$,
\begin{equation*}
    v_0^{\ast} = \frac{\lambda_0}{t_0} 
\end{equation*}
and computing $\Gamma$ in terms of $v_0^{\ast}$ yields
\begin{equation*}
    \Gamma = \frac{v_0^{\ast}}{U_{\theta}} = \frac{6\pi h_0^3 q_0^3}{\Theta^3}.
\end{equation*}
Relating both with each other yields
\begin{equation*}
    \frac{\chi 3\lambda h_0^3 q_0^4}{\Theta^3} = \frac{6\pi h_0^3 q_0^3}{\Theta^3},
\end{equation*}
and with most of the terms canceling one obtains
\begin{equation*}
    \lambda = \frac{2\pi}{q_0\chi}, 
\end{equation*}
which in fact states that if the wavelength $\chi^{-1}2\pi/q_0 < \lambda$ rivulets should form. 
\JH{Change in paper?}
}

\item[ \textbf{\underline{Comment 5.}}]
{
The thin film equation relies on a local approximation for the interface potential and disjoining pressure. 
Notice that to first order in non-local effects, the surface tension entering the thin film equation adopts a film thickness dependence which could potentially affect the dynamics. 
Particularly, as far as the parallel correlation length $q_0$ is referred, the non-local effects provide an upper bound equal to the inverse bulk correlation length. 
This could be a significant effect in polymer thin films (c.f. Benet et al. jpc-c 118, 22079, 2014 and the related discussion on dynamical effects Pahlavan et al., jfm, 845, 642, 2018).
}

\item[ \textbf{{Answer}}]
{
That is indeed a very interesting point.
In fact, we know the second reference very well from our own work~\cite{PhysRevE.104.034801}.
It is an appealing model, and we look forward to discussing it in further details in future publications.
We therefore added the following to the conclusion 
\\
\textcolor{red}{...}
}

\end{itemize}

\bibliographystyle{abbrv}
\bibliography{Ref}

\end{document}

### 2022-10-03 Reply_RefereeC.tex

\documentclass[12pt,english]{article}

\usepackage{natbib}

\usepackage{graphics,graphicx,dcolumn,bm,fleqn,epic,eepic,float}
\usepackage{amssymb,amsmath,multirow,rotate,rotating,color}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
%\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\tikzset{fontscale/.style = {font=\relsize{#1}}}
\usetikzlibrary{calc}
\makeatother

\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\eqnref}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\ts}{\textsuperscript}

\definecolor{tuered}{RGB}{214,0,74}

\newcommand{\todo}[1]{\textbf{\textcolor{tuered}{ TODO: #1}}}

\newcommand{\vectornorm}[1]{\left|\left|#1\right|\right|}

\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\uvec}[1]{\hat{\vec{#1}}}
\newcommand{\tensor}[1]{\mathbf{#1}}

\definecolor{pyblue}{HTML}{1F77B4}
\definecolor{pyorange}{HTML}{FF7F0C}
\definecolor{pygreen}{HTML}{2CA02C}
\definecolor{pyred}{HTML}{D62728}

\newcommand{\JH}[1]{\textcolor{blue}{JH: #1}}
\begin{document}

% The referee PDF has been generated from r239 -- 'make referee' command.

\section*{Reply to Referee C}
We thank the Referee for his/her report on our manuscript.
We are glad to read that he/she finds the study scientifically sound and credible and 
the manuscript well written. Based on his/her important remarks, we have 
prepared a revised version which we hope will be more convincing also for what concerns
its impact and interest for the readership of Physical Review Letters.
Hereafter detailed answers to the various questions raised are reported. All changes 
in the text are edited in red colour, for the sake of clarity.

\begin{itemize}

\item[ \textbf{\underline{Comment 1.}}]
{ 
However, I feel that the
results presented lack a sufficient breadth and impact so as to
warrant publication in Physical Review Letters - provided that one has
a suitable substrate, I do not see how would the transport of a fluid
by way of transient rivulets surpass the transport by way of droplets
in practice.
}

\item[ \textbf{{Answer}}]
{ 
We say nowhere that the rivulets would transport fluid more efficiently. Actually 
we do not talk about transport at all. The focus, here, is not on sliding or similar force-driven processes, but 
on dewetting and, in particular, on the different dewetting {\it morphologies}. 
It is true, on the other hand, that rivulets are metastable, but, as 
we showed, their lifetime can be extended increasing the pattern speed
(therefore enabling treatment, e.g. curing, of the substrate to 
fix a given pattern).
Concerning the breadth and impact to warrant publication in Physical Review Letter, as we think we stressed extensively in the introduction,
the problem of controlling dewetting, besides being of fundamental interest in Fluid Dynamics (which represents an important part of the 
PRL readership), it is crucially relevant for applications in 
nanoprinting (including printable electronics). 
This is witnessed by the various publications in PRL on this and closely related problems. To cite but a few recent ones: J.C. Fern\'andez-Toledano et al, "How wettability controls nanoprinting",
{\it Phys. Rev. Lett.} {\bf 124} 224503 (2020); A.A. Pahlavan et al,
"Evaporation of binary-mixture liquid droplets: the formation of picoliter pancakelike shapes", {\it Phys. Rev. Lett.} {\bf 127}, 024501 (2021); C. Clavaud et al, "Modification of the fluctuation dynamics of ultrathin wetting films", {\it Phys. Rev. Lett.} {\bf 126}, 228004 (2021).
\JH{We have to make sure to strongly doubt the competence of Ref C in the letter to the editor! I guess this will be the only chance for us to get the paper through/}
}

\item[ \textbf{\underline{Comment 2.}}]
{ 
The core of the manuscript is a numerical study which includes a
number of model parameters and specific choices of their values, say
$\theta_0$, $ \delta \theta$, $\delta$, $h_0$, 
the square pattern itself, the
orientation of the velocity of the contact angle, etc. Naturally,
these choices need to be made, but drawing conclusions from just a few
sets is, in my opinion, premature.
For example, I imagine that the rivulets will not form if $\delta\theta$ were too small, or too small relative to $\theta_0$. 
The authors focused on the importance of the speed of the pattern and on its wavelength but they left most other parameters fixed to a single value, the reasons for their choice being unclear.
}

\item[ \textbf{{Answer}}]
{ 
The Referee is right. Indeed there are of course several parameters 
that may influence the physics of the problem. In this (first) contribution, though,
our aim is to single out the factor determining the novel effect found (the 
droplet-rivulet duality), namely
the pattern time dependence (and, hence, the 'wave' speed). 
One may expect of course that there is a dependence on $\delta \theta$ and $\theta_0$, but this would apply to the static case. 
A systematic study of the full parameter space would then deserve a dedicated, 
extended, work that goes somehow beyond the goal of the present paper and a typical PRL contribution.
Nevertheless, we agree with the Referee that it is appropriate to add further details, therefore we commented in the text 
on the choice of the checkerboard pattern and of $\theta_0$ and we have added 
results at changing $\delta \theta$ in a Supplemental Material section.

{\bf ANDREA: Stefan, we do have these data, right? I think to remember that you ran the simulations}

%The observation of the referee is correct.
%Indeed, the difference in contact angle amounts to a net force on the liquid.
%This force can be large enough to actuate %droplets~\cite{doi:10.1021/acs.langmuir.5b02335}.

%The thin film equation is valid only in the regime where $\theta \ll \pi/2$.
%Choosing $\theta_0 = 20^{\circ}$ and a $\Delta\theta$ of the same magnitude %therefore ensures that we are well within the predictability of our model.
%Therefore we find that our value of $\theta_0$ is a good compromise to satisfying %the constraints.

%Most of our results are given in terms of $t_0$ and $q_0$.
%Both contain parameters we choose to set up our numerical experiments. 
%We supply an equation to calculate them and have no evidence to believe that our theoretical assumptions are incorrect.
%Could the referee please elaborate why he/she thinks we overlook something?

%\textcolor{pyorange}{Stefan}: I would put the results we have from the x-only %velocity run here.
%They kind a answer what happens if $\Delta\theta$ becomes larger (rivulets life for %a very short amount of time only).
}

\item[ \textbf{\underline{Comment 3.}}]
{ 
Also unclear is how does the substrate patterning scale $2\pi/q_\theta$ compare with the scale of homogeneous dewetting $2\pi/q_0$.
I tried hard to understand whether the different cases of $\lambda$ discussed in the paper agree with $2\pi/q_0$ but I was unable to do so. 
How would the film behave if the dynamics of the film were controlled primarily by spinodal dewetting and not by the contact-angle pattern?
At the same time, if the two characteristic lengthscales ($=$ that of the spinodal dewetting and that of the patterned substrate) are suitably synchronized, perhaps rivulets can be rendered permanent rather than transient? Or is the dewetting, once initiated, immanently irreversible even for a
time-dependent contact-angle pattern like the one studied in LM17723?
}

\item[ \textbf{{Answer}}]
{
We apologize for having lacked thoroughness not providing the numerical 
value of $q_0$ (of which we reported the expression, though) to compare with the 
other characteristic scales. Plugging in the values of $\Theta = \theta_0 + \delta \theta$, 
$h_0$ and $h_{\ast}$ we get $q_0 \approx 0.13 h_0^{-1}$, whence 
$\lambda_0 = 2\pi/q_0 \approx 50 h_0$, so it corresponds approximately to the 
shortest pattern wavelength considered. The pattern-driven instability overwhelms the spinodal instability because it is active even on an initially
flat film 
(i.e., where the initial perturbation $|\delta h_0| \rightarrow 0$) 
\cite{KonnurPRL2000,KarguptaLangmuir2000,KarguptaPRL2001}; ideally one would need to have a vanishing 
contact angle mismatch in order to see the spinodal dewetting, namely $\delta \theta \sim \delta h_0/h_0$,
which is also somehow obvious, but it would eventually deprive the pattern of meaning. 
The emergence of rivulets is observed even for $\lambda \approx \lambda_0$, as we show in a new figure
(in the Supplemental Material), but their nature is still metastable.

{\bf ANDREA: Stefan your input is needed here, too. Did you make the simulations/figures, with the 
properly defined $\Gamma$ for $\lambda \approx 2 \pi/q_0$?}
}
%We are sorry for creating confusion with the choice of our variables.
%Let us call $\lambda_0 = 2\pi/q_0$ and rephrase Eq.~(11) in terms of $\lambda_0$ %using $v_0^{\ast}$,
%\begin{equation*}
%    v_0^{\ast} = \frac{\lambda_0}{t_0}, 
%\end{equation*}
%computing $\Gamma$ in terms of $v_0^{\ast}$ yields
%\begin{equation*}
%    \Gamma = \frac{v_0^{\ast}}{U_{\theta}} = \frac{6\pi h_0^3 q_0^3}{\Theta^3}.
%\end{equation*}
%Setting this result equal with Eq.~(11) in the manuscript we have
%\begin{equation*}
%    \frac{\chi 3\lambda h_0^3 q_0^4}{\Theta^3} = \frac{6\pi h_0^3 q_0^3}{\Theta^3},
%\end{equation*}
%with most of the terms canceling
%\begin{equation*}
%    \lambda = \frac{2\pi}{q_0\chi}, 
%\end{equation*}
%which in fact state that if the wavelength $\chi^{-1}2\pi/q_0 < \lambda$ rivulets %should form. 
%}

%\item[ \textbf{\underline{Comment 4.}}]
%{ 
%How would the film behave if the dynamics of the film were controlled primarily by %spinodal dewetting and not by the contact-angle pattern?
%}

%\item[ \textbf{{Answer}}]
%{ 
%We thank the referee for raising this question.
%The straightforward answer is we can reproduce the structure factor of a spinodally %dewetting thin film which is given by
%\begin{equation*}
%    S(q,t) = S_0 e^{2\omega(q)t},
%\end{equation*}
%where is $S_0$ is a constant factor and 
%\begin{equation*}
%    \omega(q) = \frac{1}{t_0}\left[2\left(\frac{q}{q_0}\right)^2 - %\left(\frac{q}{q_0}\right)^4\right],
%\end{equation*}
%}
%which can be found in ref.~\cite{PhysRevE.104.034801}, Fig~1.
%After the generation of droplets, we observe a coarsening scaling according to a %powerlaw.

%\item[ \textbf{\underline{Comment 5.}}]
%{ 
%At the same time, if the two characteristic lengthscales ($=$ that of the spinodal %dewetting and that of the patterned substrate) are suitably synchronized, perhaps %rivulets can be rendered permanent rather than transient? Or is the dewetting, once %initiated, immanently irreversible even for a
%time-dependent contact-angle pattern like the one studied in LM17723?
%}

%\item[ \textbf{{Answer}}]
%{ 
%This is an interesting comment.
%To our understanding, this is not the case as shown in Fig.~5 of the manuscript.
%We observe a saturation like effect for high pattern velocity.
%Independent of the velocities, the rivulet admits a varicose instability, which %within our study was not possible to overcome.
%We hypothesize that another substrate pattern could ensure indefinite rivulet %stability.
%However as we do not have an intuition, testing N-patterns would be beyond the scope %of this work.

%For further details on the scale synchronization, we would point towards the answer %to Comment 4.
%}

\item[ \textbf{\underline{Comment 4.}}]
{ 
Many of the numerical results are supported by scaling estimates. I
like these arguments, but the agreement is hardly convincing. For
example, the linear and the square scaling laws in Fig. 2 each cover a
small range (much less than a tenfold variation) and so it is hard to
see whether they really apply. 
The same goes for the rivulet lifetime in Fig. 5 where the trend is OK but most likely a scaling law different from $\log(v_{\theta})$ would do as well in the range of $\tau_{riv}$ covered by the numerical data.
}

\item[ \textbf{{Answer}}]
{ 
We are well aware that the parameter ranges are not too wide, but 
of course our method (as any other) has to cope with limitations. 
For example, the range of achievable wavelengths is limited from below 
by the need to stay in the lubrication regime, and from above by the size of the system (i.e. by computing resources). We could actually increase the system size and thus push further the upper limit of $\lambda$, but this would only extend the $\lambda^2$ scaling range. {\bf ANDREA: May we try one run on a bigger 
system? Being 1d it shouldn't take too long, should it? It would be also interesting to try a smaller $\Theta$: my handwaving argument on comparing times tells that it should extend a bit the linear, $\sim \lambda$,  scaling range.}
As for the rivulet lifetimes, analogously, for reasons intrinsic to the stability of the numerical method, much higher pattern speeds cannot be reached 
(in particular one has to comply with the condition $\Gamma \ll 5 \times 10^2$).
We tend to disagree, instead, with the comment that any other scaling 
law would be equivalently good. Essentially because the logarithm scaling is 
not a fit, it is the result of a derivation based on plausible theoretical arguments, that 
is 'OK' with the numerical data.
We think, anyhow, that the Referees' concerns are legitimate and we have, therefore, added 
comments of caution about the scaling laws in the revised text.
Let us remark, though, that even in real microfluidic systems, 
one cannot expect too wild (and wide) variation of lengths and velocities.
In fact, we would be glad if our pioneering study might motivate further work 
in this direction, hopefully confirming our findings on an extended parameter 
range. Of course, that is more likely to happen if our message is conveyed
by a contribution in a high impact journal such as PRL. 
}

\end{itemize}

\bibliographystyle{abbrv}
\bibliography{Ref}

\end{document}
